# kronmueller-barr-2007

Repository of data and scripts for:

Kronmüller, E., &amp; Barr, D. J. (2007). [Perspective-free pragmatics: Broken precedents and the recovery-from-preemption hypothesis.](https://doi.org/10.1016/j.jml.2006.05.002) *Journal of Memory and Language*, *56*, 436--455.

Currently this repository contains only response time data for Experiment 2.

# Codebooks

## Experiment 2

- 1792 total observations from 56 subjects and 32 stimuli (*Note*: three observations were removed; see p. 447 of the manuscript)

### Response Time

```{r rt_codebook, message = FALSE, results = 'markdown', echo = FALSE}
suppressPackageStartupMessages(library("tidyverse"))

tribble(~column, ~description,
        "`subj`", "unique subject identifier",
        "`item`", "unique stimulus item identifier",
        "`spkr`", "whether the speaker was old or new",
        "`prec`", "whether the precedent was broken or maintained",
        "`load`", "whether the subject was under cognitive load",
        "`rt_trunc`", "response time, truncated at 5171 ms",
        "`rt_raw`", "response time, not truncated") %>%
  knitr::kable("markdown")
```

#### Table 3 (p. 448)

*Note:* The values in Table 3 are based on the raw (non-truncated) values.

```{r tbl-3}
library("tidyverse")

kb07 <- readRDS("kb07_rt.rds")

kb07 %>%
  group_by(spkr, prec, load) %>%
  summarize(mean = mean(rt_raw), sd = sd(rt_raw)) %>%
  ungroup() %>%
  knitr::kable("markdown", digits = 0)
```

#### Analysis by Subject (p. 448)

```{r f1-f2, echo = TRUE}
subj_means_trunc <- kb07 %>%
  group_by(subj, spkr, prec, load) %>%
  summarize(rt = mean(rt_trunc)) %>%
  ungroup() %>%
  mutate(spkr = factor(spkr),
         prec = factor(prec),
         load = factor(load))

by_subj <- ez::ezANOVA(subj_means_trunc,
            rt,
            wid = subj,
            within = .(spkr, prec, load),
            type = 3)$ANOVA

by_subj %>%
  knitr::kable("markdown", digits = 2, row.names = FALSE) 
```

#### Analysis by Item (p. 448)

```{r exp2-rt-by-item}
item_means_trunc <- kb07 %>%
  group_by(item, spkr, prec, load) %>%
  summarize(rt = mean(rt_trunc)) %>%
  ungroup() %>%
  mutate(spkr = factor(spkr),
         prec = factor(prec),
         load = factor(load))

by_item <- ez::ezANOVA(item_means_trunc,
            rt,
            wid = item,
            within = .(spkr, prec, load),
            type = 3)$ANOVA

by_item %>%
  knitr::kable("markdown", digits = 2, row.names = FALSE)
```
